Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-06 doc/paper.Rmd
re-phrasing error rates

Bullet matching methods are usually based on these associated signatures. \citet{chu2013} use an automatic method for counting consecutive matching striae (CMS). The authors report an error rate of 52% of the known same source lands comparisons as misidentified (false negative) and zero false positives for known different source lands. \citet{ma2004} and \citet{vorburger2011} discuss CCF (cross-correlation function) and its discriminating power and applicability for same-source analyses of bullets, but do not provide any error rates in their discussion. \citet{aoas} use multiple features like CCF, CMS, D (distance measure) etc in a random forest based method and compare every land against every other land of  digitised versions of Hamby 252 and Hamby 44 \citep{hamby} published on the NIST Ballistics Database \citep{nist}. The authors report an out-of-bag overall error rate of 0.46%, comprised of a false positive error rate of 30.05% and a false negative rate of 0.026%.

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks. \citet{chumbley} compare two toolmarks for same-source. The data for this study was obtained from 50 sequentially manufactured screwdriver tips. \citet{chumbley} report error rates for markings made by the tips at different angles. For markings made under a 30 degree the authors  report an average false negative error rate of 0.023  and an average false positive error rate of 0.09. For other angles the error rates for false negatives stay the same while the rate of false positives decreases to 0.01. \hh{are the angles steeper?} 
The paper by \citet{hadler} is based on the same data but the authors focus on  markings made under the same angle. The error rates associated with the deterministic version of the score are  0.06 for false  negatives and a false poisitive error rate of 0.

>>>>

Bullet matching methods are usually based on these associated signatures. \citet{chu2013} use an automatic method for counting consecutive matching striae (CMS). The authors report an error rate of 52% of the known same source lands comparisons as misidentified (false negative) and zero false positives for known different source lands. \citet{ma2004} and \citet{vorburger2011} discuss CCF (cross-correlation function) and its discriminating power and applicability for same-source analyses of bullets, but do not provide any error rates in their discussion. \citet{aoas} use multiple features like CCF, CMS, D (distance measure) etc in a random forest based method and compare every land against every other land of  digitised versions of Hamby 252 and Hamby 44 \citep{hamby} published on the NIST Ballistics Database \citep{nist}. The authors report an out-of-bag overall error rate of 0.46%, comprised of an error rate of 30.05% of  same-source pairs that were not identified and an error rate of 0.026% of different-source pairs that were incorrectly identified as same-source.

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks. \citet{chumbley} compare two toolmarks for same-source. The data for this study was obtained from 50 sequentially manufactured screwdriver tips. \citet{chumbley} report error rates for markings made by the tips at different angles. For markings made under a 30 degree the authors  report an average false negative error rate of 0.023  and an average false positive error rate of 0.09. For other angles the error rates for false negatives stay the same while the rate of false positives decreases to 0.01. \hh{are the angles steeper?} 
The paper by \citet{hadler} is based on the same data but the authors focus on  markings made under the same angle. The error rates associated with the deterministic version of the score are  0.06 for false  negatives and a false positive error rate of 0.
